COG-ED Manuscript

### 2022-06-07 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 2.9

To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package[@Kuznetsova2017]. 
We will apply restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to Lorah[-@Lorah2018].
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

>>>>

To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package[@Kuznetsova2017]. 
We will apply restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
Within the model, we will therefore control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to Lorah[-@Lorah2018].
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
